Bird beak's elaboration and exploration

### 2022-10-18 Analysis/11-variance_partitioning.Rmd
Update 11-variance_partitioning.Rmd

```{r, echo = FALSE, fig.height = 16, fig.width = 4}
## Plotting all the variance elements
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(second_model_results, second_model_run, group.cols = c(clade_cols, "residuals" = "darkgrey"), relative = FALSE, plot = "var boxplot")
```

@@

```{r, echo = FALSE, fig.height = 16, fig.width = 4}
## Plotting all the variance elements
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(second_model_results, second_model_run, group.cols = c(clade_cols, "residuals" = "darkgrey"), relative = FALSE, plot = "log var boxplot")
```

@@

```{r, echo = FALSE, fig.height = 4, fig.width = 8}
## Plotting the variance with different data
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(birds_data, model, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = c("standard error", "log standard error"))
```

@@

```{r, echo = FALSE, fig.height = 4, fig.width = 8}
## Plotting the variance with different data
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(birds_data, model, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = c("corrected var boxplot", "corrected var by n"))
```

>>>>

```{r, echo = FALSE}
## Plotting all the variance elements
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(second_model_results, second_model_run, group.cols = c(clade_cols, "residuals" = "darkgrey"), relative = FALSE, plot = "var boxplot")
```

@@

```{r, echo = FALSE}
## Plotting all the variance elements
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(second_model_results, second_model_run, group.cols = c(clade_cols, "residuals" = "darkgrey"), relative = FALSE, plot = "log var boxplot")
```

@@

```{r, echo = FALSE, fig.height = 6, fig.width = 12}
## Plotting the variance with different data
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(birds_data, model, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = c("standard error", "log standard error"))
```

@@

```{r, echo = FALSE, fig.height = 6, fig.width = 12}
## Plotting the variance with different data
par(mar = c(5, 6, 4, 2) + 0.1)
plot.decompose.var(birds_data, model, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = c("corrected var boxplot", "corrected var by n"))
rm(birds_data)
rm(model)
```
